---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidypass

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

A tidy R interface to the [Postpass](https://github.com/woodpeck/postpass-ops) service. Allows you to use dplyr syntax to retrieve OpenStreetMap data using [`{dbplyr}`](https://dbplyr.tidyverse.org/). Postpass is a nice alternative to [Overpass Turbo](https://overpass-turbo.eu/) that is faster and more versatile because it uses a Postgres database in the background.

## Installation

You can install the development version of tidypass from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("jslth/tidypass")
```

## Example

This is a basic example which extracts all fast food restaurants in Karlsruhe along with their stated cuisine. As you can see, this is mostly written using dplyr. Spatial filters are a bit more complicated but also mostly follow dplyr syntax.

```{r build, warning=FALSE, message=FALSE}
library(tidypass)
library(sf)

# Boundaries of Karlsruhe
bbox <- st_as_sfc(st_bbox(c(
  xmin = 8.34,
  xmax = 8.46,
  ymin = 48.97,
  ymax = 49.03
)))

query <- pp_tbl("point") |>
  filter(amenity == "fast_food" & geom %&&% !!pg_bbox(bbox)) |>
  select(cuisine, name, geom)
```

Since Postpass works with SQL, the query is translated to Postgres SQL through `dbplyr`.

```{r query}
query
```

Postpass employs a queue system where you are assigned a different priority depending on the estimated size of your query. If the total amount of scanned data is too high, you are assigned a medium or slow queue, which can take a while. Fast food restaurants in Karlsruhe are very fast.

```{r explain}
explain(query)
```

Data can be extracted using the `collect` method. This sends the SQL query to the Postpass server.

```{r collectl}
fast_food <- collect(query)
```

```{r}
plot(bbox)
plot(st_geometry(fast_food), add = TRUE)
```

```{r include=FALSE}
knitr::plot_crop("man/figures/README-unnamed-chunk-2-1.png")
```

